A pipeline to analyse time-course gene expression data

### 2019-07-25 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

@@

\begin{verbatim}
label: enrichment_analysis (with options) 
List of 2
 $ results: chr "hide"
 $ message: logi FALSE

Quitting from lines 1124-1138 (manuscript.Rmd) 
Error in getBM(attributes = c("ensembl_gene_id", "entrezgene"), filters = "refseq_mrna",  : 
  Invalid attribute(s): entrezgene 
Please use the function 'listAttributes' to get valid attribute names
Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> getBM
\end{verbatim}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-5-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-11-1} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-16-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-22-1} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-29-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-29-2} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-31-1} \end{center}

@@

@@

\begin{verbatim}
## R version 3.6.0 (2019-04-26)
## Platform: x86_64-pc-linux-gnu (64-bit)
## Running under: Ubuntu 19.04
## 
## Matrix products: default
## BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.8.0
## LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.8.0
## 
## locale:
## [1] C
## 
## attached base packages:
##  [1] stats4    parallel  splines   stats     graphics  grDevices utils    
##  [8] datasets  methods   base     
## 
## other attached packages:
##  [1] RColorBrewer_1.1-2   moanin_0.0.0         topGO_2.32.0        
##  [4] SparseM_1.77         GO.db_3.6.0          AnnotationDbi_1.42.1
##  [7] IRanges_2.14.12      S4Vectors_0.18.3     graph_1.58.2        
## [10] viridis_0.5.1        viridisLite_0.3.0    KEGGprofile_1.22.0  
## [13] RCurl_1.95-4.12      bitops_1.0-6         NMF_0.21.0          
## [16] Biobase_2.40.0       BiocGenerics_0.26.0  cluster_2.0.9       
## [19] rngtools_1.3.1.1     pkgmaker_0.27        registry_0.5-1      
## [22] ggplot2_3.1.1        biomaRt_2.36.1       BiocStyle_2.8.2     
## [25] kableExtra_1.1.0     knitr_1.22           limma_3.36.5        
## [28] usethis_1.5.0        devtools_2.0.2       rmarkdown_1.12      
## 
## loaded via a namespace (and not attached):
##  [1] colorspace_1.4-1        rprojroot_1.3-2        
##  [3] XVector_0.20.0          fs_1.3.1               
##  [5] rstudioapi_0.10         remotes_2.0.4          
##  [7] bit64_0.9-7             ClusterR_1.1.9         
##  [9] KEGG.db_3.2.3           xml2_1.2.0             
## [11] codetools_0.2-16        doParallel_1.0.14      
## [13] pkgload_1.0.2           ade4_1.7-13            
## [15] gridBase_0.4-7          png_0.1-7              
## [17] FD_1.0-12               readr_1.3.1            
## [19] compiler_3.6.0          httr_1.4.0             
## [21] backports_1.1.4         Matrix_1.2-17          
## [23] assertthat_0.2.1        lazyeval_0.2.2         
## [25] cli_1.1.0               htmltools_0.3.6        
## [27] prettyunits_1.0.2       tools_3.6.0            
## [29] gmp_0.5-13.5            gtable_0.3.0           
## [31] glue_1.3.1              reshape2_1.4.3         
## [33] dplyr_0.8.0.1           BiocWorkflowTools_1.6.2
## [35] Rcpp_1.0.1              Biostrings_2.48.0      
## [37] NMI_2.0                 ape_5.3                
## [39] nlme_3.1-139            iterators_1.0.10       
## [41] xfun_0.6                stringr_1.4.0          
## [43] ps_1.3.0                testthat_2.1.1         
## [45] rvest_0.3.3             gtools_3.8.1           
## [47] XML_3.98-1.19           zlibbioc_1.26.0        
## [49] MASS_7.3-51.4           scales_1.0.0           
## [51] hms_0.4.2               curl_3.3               
## [53] yaml_2.2.0              memoise_1.1.0          
## [55] gridExtra_2.3           TeachingDemos_2.10     
## [57] stringi_1.4.3           RSQLite_2.1.1          
## [59] desc_1.2.0              foreach_1.4.4          
## [61] permute_0.9-5           pkgbuild_1.0.3         
## [63] bibtex_0.4.2            geometry_0.4.1         
## [65] rlang_0.4.0             pkgconfig_2.0.2        
## [67] matrixStats_0.54.0      evaluate_0.13          
## [69] lattice_0.20-38         purrr_0.3.2            
## [71] bit_1.1-14              processx_3.3.1         
## [73] tidyselect_0.2.5        plyr_1.8.4             
## [75] magrittr_1.5            bookdown_0.9           
## [77] R6_2.4.0                DBI_1.0.0              
## [79] mgcv_1.8-28             pillar_1.3.1           
## [81] withr_2.1.2             abind_1.4-5            
## [83] KEGGREST_1.20.2         tibble_2.1.1           
## [85] crayon_1.3.4            progress_1.2.0         
## [87] grid_3.6.0              blob_1.1.1             
## [89] callr_3.2.0             git2r_0.25.2           
## [91] vegan_2.5-4             digest_0.6.18          
## [93] webshot_0.5.1           xtable_1.8-4           
## [95] munsell_0.5.0           magic_1.5-9            
## [97] sessioninfo_1.1.1
\end{verbatim}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(devtools)}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"NelleV/moanin"}\NormalTok{, }\DataTypeTok{dependencies=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##   
   checking for file '/tmp/RtmpHrqs5v/remotes341f57a29b/NelleV-moanin-205e154/DESCRIPTION' ...

v  checking for file '/tmp/RtmpHrqs5v/remotes341f57a29b/NelleV-moanin-205e154/DESCRIPTION'
##

-  preparing 'moanin':
##    checking DESCRIPTION meta-information ...

v  checking DESCRIPTION meta-information
##

-  checking for LF line-endings in source and make files and shell scripts
##

-  checking for empty or unneeded directories
## -  looking to see if a 'data/datalist' file should be added
##

-  building 'moanin_0.0.0.tar.gz' (3.5s)
##

## 
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(moanin)}
\end{Highlighting}
\end{Shaded}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-6-1} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-13-1} \end{center}

@@

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-24-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-30-1} \end{center}

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-30-2} \end{center}

@@

@@

\begin{center}\includegraphics{reports/manuscript_files/figure-latex/unnamed-chunk-33-1} \end{center}

@@

\begin{verbatim}
## R version 3.6.0 (2019-04-26)
## Platform: x86_64-pc-linux-gnu (64-bit)
## Running under: Ubuntu 19.04
## 
## Matrix products: default
## BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.8.0
## LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.8.0
## 
## locale:
## [1] C
## 
## attached base packages:
##  [1] stats4    parallel  splines   stats     graphics  grDevices utils    
##  [8] datasets  methods   base     
## 
## other attached packages:
##  [1] RColorBrewer_1.1-2   moanin_0.0.0         topGO_2.32.0        
##  [4] SparseM_1.77         GO.db_3.6.0          AnnotationDbi_1.42.1
##  [7] IRanges_2.14.12      S4Vectors_0.18.3     graph_1.58.2        
## [10] viridis_0.5.1        viridisLite_0.3.0    KEGGprofile_1.22.0  
## [13] RCurl_1.95-4.12      bitops_1.0-6         NMF_0.21.0          
## [16] Biobase_2.40.0       BiocGenerics_0.26.0  cluster_2.0.9       
## [19] rngtools_1.3.1.1     pkgmaker_0.27        registry_0.5-1      
## [22] ggplot2_3.1.1        biomaRt_2.36.1       BiocStyle_2.8.2     
## [25] kableExtra_1.1.0     knitr_1.22           limma_3.36.5        
## [28] usethis_1.5.0        devtools_2.0.2       rmarkdown_1.12      
## 
## loaded via a namespace (and not attached):
##  [1] colorspace_1.4-1        rprojroot_1.3-2        
##  [3] XVector_0.20.0          fs_1.3.1               
##  [5] rstudioapi_0.10         remotes_2.0.4          
##  [7] bit64_0.9-7             ClusterR_1.1.9         
##  [9] KEGG.db_3.2.3           xml2_1.2.0             
## [11] codetools_0.2-16        doParallel_1.0.14      
## [13] pkgload_1.0.2           ade4_1.7-13            
## [15] gridBase_0.4-7          png_0.1-7              
## [17] FD_1.0-12               readr_1.3.1            
## [19] compiler_3.6.0          httr_1.4.0             
## [21] backports_1.1.4         Matrix_1.2-17          
## [23] assertthat_0.2.1        lazyeval_0.2.2         
## [25] cli_1.1.0               htmltools_0.3.6        
## [27] prettyunits_1.0.2       tools_3.6.0            
## [29] gmp_0.5-13.5            gtable_0.3.0           
## [31] glue_1.3.1              reshape2_1.4.3         
## [33] dplyr_0.8.0.1           BiocWorkflowTools_1.6.2
## [35] Rcpp_1.0.1              Biostrings_2.48.0      
## [37] NMI_2.0                 ape_5.3                
## [39] nlme_3.1-139            iterators_1.0.10       
## [41] xfun_0.6                stringr_1.4.0          
## [43] ps_1.3.0                testthat_2.1.1         
## [45] rvest_0.3.3             gtools_3.8.1           
## [47] XML_3.98-1.19           zlibbioc_1.26.0        
## [49] MASS_7.3-51.4           scales_1.0.0           
## [51] hms_0.4.2               yaml_2.2.0             
## [53] curl_3.3                memoise_1.1.0          
## [55] gridExtra_2.3           TeachingDemos_2.10     
## [57] stringi_1.4.3           RSQLite_2.1.1          
## [59] desc_1.2.0              foreach_1.4.4          
## [61] permute_0.9-5           pkgbuild_1.0.3         
## [63] bibtex_0.4.2            geometry_0.4.1         
## [65] rlang_0.3.4             pkgconfig_2.0.2        
## [67] matrixStats_0.54.0      evaluate_0.13          
## [69] lattice_0.20-38         purrr_0.3.2            
## [71] bit_1.1-14              processx_3.3.1         
## [73] tidyselect_0.2.5        plyr_1.8.4             
## [75] magrittr_1.5            bookdown_0.9           
## [77] R6_2.4.0                DBI_1.0.0              
## [79] mgcv_1.8-28             pillar_1.3.1           
## [81] withr_2.1.2             abind_1.4-5            
## [83] KEGGREST_1.20.2         tibble_2.1.1           
## [85] crayon_1.3.4            progress_1.2.0         
## [87] grid_3.6.0              vegan_2.5-4            
## [89] blob_1.1.1              callr_3.2.0            
## [91] git2r_0.25.2            digest_0.6.18          
## [93] webshot_0.5.1           xtable_1.8-4           
## [95] munsell_0.5.0           magic_1.5-9            
## [97] sessioninfo_1.1.1
\end{verbatim}
